---
title: 'Forecasting covid-19 hospital admission in UK'
author:
  - "Studend Number:21114834   Module Number: BST832"
  - "Lecturer Name: Dr Bahman Rostami-Tabar "
date: "07 May 2022"
output:
  pdf_document: 
    latex_engine: xelatex
    toc: yes
bibliography: mybib.bib
csl: harvard-cardiff-university.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,eval = TRUE, warning = FALSE, message = FALSE, 
                      out.width = "70%", fig.align = 'center', fig.pos = 'H')
library(fpp3)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(kableExtra)
library(gridExtra)
library(janitor)
library(GGally)
```



```{r data-introduce, include=FALSE}
covid19_uk <- read_csv(file = "data/covid19_uk.csv")
#col_types = cols(ID = col_date(format = "%d/%m/%Y")))                       

covid19_uk$date <- as_date(covid19_uk$date,format="%d/%m/%Y")
```

describe dataset.

  

#   Part A- key feature     

## Dataset Covid19 UK:

## Check data quality:

```{r quality-check, include=FALSE}
covid19_uk %>% anyNA()
covid19_uk %>% duplicated() %>% sum()
covid19_tsb<-as_tsibble(covid19_uk, index= date)

```

describe data

## Prelimary analysis:

### Hospital timeseries visualisation

```{r data-vis, options}
covid19_tsb %>% ggplot(mapping=aes(x= date, y=hospital_admission))+ geom_point()+geom_line()+ ggthemes::theme_clean()

```

A time-series plot is a commonly used graphical tool useful for examining the underlying long-term pattern of a time series. Time (days, months, years, etc.) is plotted on the horizontal axis, and the series of interest is plotted on the vertical axis. Here in this time series visualization 
For the time series, I utilized date and hospital admission.

```{r SeasonalPlot, fig.cap="weekly cases"}
hospital_adm<-covid19_tsb %>% select(hospital_admission)
hospital_adm %>% gg_season(period = "week") + geom_point() +ggthemes::theme_clean()
```

```{r Autocorrelation}
hospital_adm %>% ACF(lag_max = 28) %>% autoplot()+ggthemes::theme_clean()
```


Autocorrelation is significant because it can assist us in identifying trends in our data, selecting the optimal prediction model, and appropriately evaluating the model's efficacy.


```{r PartialACF}
hospital_adm %>% PACF(lag_max = 28) %>% autoplot()+ggthemes::theme_clean()
```

### Relationship within predictors.

```{r predictors}
numeric_predictors<-covid19_tsb %>% as_tibble() %>%  select(alltest_performed,hospital_cases,all_positive_case,NHS111_call,stringency_index,apple_driving,apple_transit,apple_walking)

numeric_predictors %>% ggpairs()
```

### Relationship between admission and predictors.

```{r label, options}
admision_predictors <- covid19_tsb %>% as_tibble() %>% select(-date)

covid19_long <-  admision_predictors %>%
  pivot_longer(cols = 2:14, names_to = "predictor", values_to = "value")

ggplot(data = covid19_long, mapping = aes(x = value, y = hospital_admission)) + 
  geom_point() +
  facet_wrap(vars(predictor), ncol = 4, scales = "free")
# you can also explore c+cf: https://online.stat.psu.edu/stat510/lesson/8/8.2
```

# Forecasting

```{r point-accuracy, options}
fc_accuracy <- read_rds("result/fc_accuracy.rds")
fc_accuracy %>% select(.model, RMSE, MAE)
```

## Accuracy for each id

```{r accuracy-id, options}
fc_accuracy_id <- read_rds("result/fc_accuracy_id.rds")

fc_accuracy_id_data <- fc_accuracy_id %>% select(.id,.model,RMSE) 

ggplot(data=fc_accuracy_id_data, aes(RMSE))+
  geom_density(aes(fill=factor(.model)), alpha=.5)
```

## Accuracy for each horizon

```{r accuracy-h, options}
fc_accuracy_h <- read_rds("result/fc_accuracy_h.rds")

```


# Refrence
